abxD01 Paper

### 2015-03-11 PAPER.Rmd
Update intro

<not done>
There is a need for more knowledge about interactions between members of the community. Know that fmts work [anna’s paper], but don’t know why, except that you recover the diversity and are receiving an established community already that works. Individual probiotics have not worked with complete success [dendukuri 2005], whereas studies find that combinations of bacteria often work better than by themselves [lawley, pamer, stein, hickson 2007]. It’s also common for bacteria to change their behavior in the context of other bacterial species [Crost 2010, quorum sensing-biofilms, recognizing fellow bacterial species vs killing others, synergistic effects (sieuwerts 2010)]. Understanding the scope of relationships between bacteria in a community is necessary to learn about its response, in concert with its host, to perturbations including antibiotic-induced, pathogen invasion, probiotics doses, and diet changes, etc.

The purest way of studying these bacterial interactions is by characterizing them in the context of their whole biome [ecology citation?]. [examples of papers showing microbiomes response to antibiotics in the context of CR]

>>>>

There is a clear need for more knowledge on *C. difficile* and its interactions between members of the bacterial community in understanding colonization resistance. Fecal microbiota transplants, which have been shown to increase *Bacteroidetes* and decrease *Proteobacteria* levels in the recipient, have successfully restored colonization resistance in patients and effectively resolved their severe CDI [Seekatz et al. 2014]. Precisely how this occurs is not fully understood, but it emphasizes the strength of the community as a whole in its protective ability. Individual probiotics have not worked with complete success [dendukuri 2005]. In fact, several studies using probiotic mixtures of several bacteria find these members often work better together than by themselves [lawley, pamer, stein, hickson 2007].

It’s also common for bacteria to change their behavior in the context of other bacterial species [Crost 2010, quorum sensing-biofilms, recognizing fellow bacterial species vs killing others, synergistic effects (sieuwerts 2010)]. Understanding the scope of relationships between bacteria in a community is necessary to learn about its response, in concert with its host, to perturbations including antibiotic-induced, pathogen invasion, probiotics doses, and diet changes, etc.
